**NeuroKit2: A Python Toolbox for Neurophysiological Signal Processing**

### 2020-08-19 paper/manuscript_v3.Rmd
minor rephrase to respect inversion + version + data struc

In this section, we present two examples that illustrate the most common use-cases. The first example shows how to extract the characteristics of physiological activity during a certain time interval (not necessarily tied to a specific and sudden event). The second example represents an event-related paradigm, in which the interest lies in shorter-term physiological changes related to specific events (see **Figure 1** and **Table 1**). The example datasets are available with the package and can be downloaded using the `data()` function.

@@

This example illustrates a type of physiological analysis that we refer to as interval-related (as opposed to event-related). Interval-related analyses compute features of signal variability and activation patterns over a longer-term period of time (typically minutes). After loading the package and the example dataset, each physiological signal is processed using `bio_process()`. As we want to compute features related to the whole dataset (see **Table 3**), we can directly pass the dataframe to `bio_analyze()`, and compute the appropriate interval-related features accordingly. These include for instance the average heart and breathing rate, as well as indices of heart rate variability (HRV) and respiratory sinus arrhythmia (RSA).*NeuroKit2* allows for the fast creation of standardized and reproducible pipelines to describe this kind of physiological activity, which can be beneficial for a wide variety of applications.

>>>>

In this section, we present two examples that illustrate the most common use-cases. The first example shows how to extract the characteristics of physiological activity during a certain time interval (not necessarily tied to a specific and sudden event). The second example presents an event-related paradigm, in which the interest lies in shorter-term physiological changes related to specific events (see **Figure 1** and **Table 1**). The example datasets are available with the package and can be downloaded using the `data()` function. This utility reads comma separated values files (*.csv*) with Pandas dedicated function (*pd.read_csv()*), where each column is a different biosignal. Both examples' results are generated using the 0.0."" version release of *NeuroKit2*.

@@

Here, the aim was to illustrate a type of physiological analysis that we refer to as interval-related (as opposed to event-related). Interval-related analyses compute features of signal variability and activation patterns over a longer-term period of time (typically minutes). After loading the package and the example dataset, each physiological signal is processed using `bio_process()`. As we want to compute features related to the whole dataset (see **Table 3**), we can directly pass the dataframe to `bio_analyze()`, and compute the appropriate interval-related features accordingly. These include for instance the average heart and breathing rate, as well as indices of heart rate variability (HRV) and respiratory sinus arrhythmia (RSA).*NeuroKit2* allows for the fast creation of standardized and reproducible pipelines to describe this kind of physiological activity, which can be beneficial for a wide variety of applications.
